{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2023-10-27 paper/main.tex
fix bibiography error
remove references to strategy inference

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,setspace,enumitem,epsfig,titlesec,verbatim,color,array,eurosym,multirow}
\usepackage[sort&compress,comma,round]{natbib}
\usepackage[footnotesize,bf]{caption}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{blkarray}
\usepackage[ruled,vlined]{algorithm2e}
\smallskip % Erlaubt kleine Abstaende zwischen Paragraphen, falls es dem Seitenlayout hilft
\renewcommand{\baselinestretch}{1.3}
\newcommand{\R}{\mathbb{R}}

@@

These difficulties to learn strategies by social imitation are particularly pronounced in models of direct reciprocity. 
This literature follows Trivers' insight that individuals have more of an incentive to cooperate in social dilemmas when they interact repeatedly~\citep{trivers1971evolution}. 
In repeated interactions, individuals can condition their behavior on their past experiences with their interaction partner. 
They may use strategies such as Tit-for-Tat~\citep{rapoport:book:1965,axelrod1981evolution} or Generous Tit-for-Tat~\citep{molander:jcr:1985,Nowak1992tit} to preferentially cooperate with other cooperators. 
Such conditional strategies approximate human behavior fairly well~\citep{fischbacher:EconL:2001,Rand:TCS:2013,DalBo:AER:2019,Rossetti:ETH:2023} and they have also been documented in several other species~\citep{Carter:PRSB:2013,Schweinfurth:AnBehav:2019,Voelkl:PNAS:2015} -- although direct reciprocity is generally more difficult to demonstrate in animals~\citep{CluttonBrock:Nature:2009,Silk:CurrentBiology:2013,taborsky:CurrentBiology:2013}.
However, at the outset, it is not clear how easy it is to {\it learn} reciprocal strategies by social imitation. 
As one obstacle, individuals usually only observe other population members' actions (i.e., whether they cooperate or defect). 
In general, these observations do not suffice to infer the underlying strategies (i.e., the contingent rules that determine whether to cooperate or defect in any given situation). 
This problem is equivalent to the difficulties that arise when researchers need to estimate the participants' strategies in behavioral experiments~\citep{Rossetti:ETH:2023}. 
As another obstacle, even if others' strategies are perfectly observable, individuals might find it difficult to identify which ones have the highest payoff. 
After all, the payoff of a strategy of direct reciprocity is not determined by the outcome of any single round.
Rather it is determined by how well this strategy fares over an entire sequence of rounds, against many different population members. 
In practice, such information might be both difficult to obtain and to process.

@@

\noindent
{\bf Description of the game dynamics.} We consider a well-mixed population consisting of $N$~players.
Players are randomly matched in pairs to participate in a repeated donation game~\citep{sigmund2010calculus}.
Each round, players can either cooperate (\(C\)) or defect (\(D\)). 
By cooperating, a player provides a benefit \(b\) to the other player at their own cost \(c\), with \(0 \!<\! c \!<\! b\). 
Thus, the players' payoffs in a single round are given by the matrix

\begin{equation}
    \begin{blockarray}{ccc}
        & \text{cooperate} & \text{defect} \\
        \begin{block}{c(cc)}
            \text{cooperate} & b - c & -c \\
            \text{defect} & b & 0 \\
        \end{block}
    \end{blockarray}.
\end{equation}
In particular, payoffs take the form of a prisoner's dilemma:
Mutual cooperation yields a better payoff than mutual defection ($b\!-\!c\!>\!0$), but each player individually prefers to defect independent of the co-player's action ($b\!>\!b\!-\!c$ and $0\!>\!-c$). 
To incorporate that individuals interact repeatedly, we assume that after each round, there is a constant continuation probability $\delta$ of interacting for another round. 
For $\delta\!=\!0$, we recover the case of a conventional (one-shot) prisoner's dilemma. 
Here, mutual defection is the only equilibrium. 
As $\delta$ increases, the game turns into a repeated game. Here, additional equilibria emerge, with some of them allowing for full cooperation~\citep{friedman:RES:1971,Akin:chapter:2016,hilbe:GEB:2015,stewart:pnas:2014}.

@@

{
{\setlength{\bibsep}{0\baselineskip}
\bibliographystyle{naturemag}
\bibliography{bibliography.bib}
}

>>>>

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,setspace,enumitem,epsfig,titlesec,verbatim,color,array,eurosym,multirow}
\usepackage[sort&compress,comma,round,numbers]{natbib}
\usepackage[footnotesize,bf]{caption}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{blkarray}
\usepackage[ruled,vlined]{algorithm2e}
\smallskip % Erlaubt kleine Abstaende zwischen Paragraphen, falls es dem Seitenlayout hilft
\renewcommand{\baselinestretch}{1.3}
\newcommand{\R}{\mathbb{R}}

@@

These difficulties to learn strategies by social imitation are particularly pronounced in models of direct reciprocity. 
This literature follows Trivers' insight that individuals have more of an incentive to cooperate in social dilemmas when they interact repeatedly~\citep{trivers1971evolution}. 
In repeated interactions, individuals can condition their behavior on their past experiences with their interaction partner. 
They may use strategies such as Tit-for-Tat~\citep{rapoport:book:1965,axelrod1981evolution} or Generous Tit-for-Tat~\citep{molander:jcr:1985,Nowak1992tit} to preferentially cooperate with other cooperators. 
Such conditional strategies approximate human behavior fairly well~\citep{fischbacher:EconL:2001,Rand:TCS:2013,DalBo:AER:2019,Rossetti:ETH:2023} and they have also been documented in several other species~\citep{Carter:PRSB:2013,Schweinfurth:AnBehav:2019,Voelkl:PNAS:2015} -- although direct reciprocity is generally more difficult to demonstrate in animals~\citep{CluttonBrock:Nature:2009,Silk:CurrentBiology:2013,taborsky:CurrentBiology:2013}.
However, at the outset, it is not clear how easy it is to {\it learn} reciprocal strategies by social imitation. 
As one obstacle, even if others' strategies are perfectly observable, individuals might find it difficult to identify which ones have the highest payoff. 
After all, the payoff of a strategy of direct reciprocity is not determined by the outcome of any single round.
Rather, it is determined by how well this strategy fares over an entire sequence of rounds, against many different population members. 
In practice, such information might be both difficult to obtain and to process.

@@

\noindent
{\bf Description of the game dynamics.} We consider a well-mixed population consisting of $N$~players.
Players are randomly matched in pairs to participate in a repeated donation game~\citep{sigmund2010calculus}.
Each round, players can either cooperate (\(C\)) or defect (\(D\)). 
By cooperating, a player provides a benefit \(b\) to the other player at their own cost \(c\), with \(0 \!<\! c \!<\! b\). 
Thus, the players' payoffs in a single round are given by the matrix
\begin{align}
\bordermatrix{%
	& C & D \cr
C &\ b-c &\ -c\  \cr
D &\ b &\ 0\ \cr
} .
\end{align}
In particular, payoffs take the form of a prisoner's dilemma:
Mutual cooperation yields a better payoff than mutual defection ($b\!-\!c\!>\!0$), but each player individually prefers to defect independent of the co-player's action ($b\!>\!b\!-\!c$ and $0\!>\!-c$). 
To incorporate that individuals interact repeatedly, we assume that after each round, there is a constant continuation probability $\delta$ of interacting for another round. 
For $\delta\!=\!0$, we recover the case of a conventional (one-shot) prisoner's dilemma. 
Here, mutual defection is the only equilibrium. 
As $\delta$ increases, the game turns into a repeated game. Here, additional equilibria emerge, with some of them allowing for full cooperation~\citep{friedman:RES:1971,Akin:chapter:2016,hilbe:GEB:2015,stewart:pnas:2014}.

@@

{
{\setlength{\bibsep}{0\baselineskip}
\bibliographystyle{naturemag}
\bibliography{bibliography.bib}
}
}
